Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-30 trunk/constantRate/ConstCompFuzzExt.tex
cleaning up sampling coins for sampler

%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  
We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.
To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.  Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.  First note that $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$.  
Define the distribution $X$ as follows:
\[X_i = 
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}_X(\cdot, \cdot)}(C)$~(\defref{def:obf}).
\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ cannot distinguish between $C$ and $C'$.  That is, $S^{\mathcal{O}_X(\cdot, \cdot)}(C) \approx S^{\mathcal{O}_X(\cdot, \cdot)}(C')$.
This is done in \lemref{lem:sim cannot distinguish}.
% the following steps:
%\begin{itemize}
%%\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
%%\item Assume that the simulator has knowledge of $C_{\mathcal{I}^c}$.
%\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the simulator's view~(\lemref{lem:codewords in I close}).
%\item The two distributions $C$ and $C'$ are indistinguishable given the simulator's view~(\bnote{this needs to be written down.})
%\item The set of codewords $C| View(S) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(S)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
%\item Any adversary given $C$ or a fresh $C'$ cannot statistically distinguish.
%\end{itemize}
\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$~(\defref{def:obf}).
\end{itemize}

Together these arguments allow us to conclude:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.  Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

\noindent
We now prove $S$ cannot distinguish between $C$ and $C'$.  
Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.  Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

@@

\subsection{Characterizing unguessable block distributions}

\defref{def:block guessable} is an inherently adaptive definition and thus a little unwieldy for a distribution.  In this section, we provide a limited characterization of sources satisfy \defref{def:block guessable} and distributions that are learnable by equality queries.

The majority of the difficulty in characterizing the definition is that different blocks may be dependent so a equality query on block $i$ may shape the distribution of block $j$.  Thus, we begin with the case of independent blocks.

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,..., W_\ell$ be a source where blocks are independent.  Let $\alpha$ be a parameter.  Let $\mathcal{I}$ be the set of blocks such that $\Hoo(W_i ) =\alpha $.  Then $W$ is a $(q, \alpha - \log (q+1), \ell - |\mathcal{I}|)$-block unguessable distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \ell - |\mathcal{I}|)$-block unguessable distribution.
\end{claim}
\begin{proof}
We ignore the blocks outside of $\mathcal{I}$ as queries on these blocks do not change the distribution of $W_i$ where $i\in \mathcal{I}$.  It suffices to show that for all $i\in \mathcal{I}, \Hav(W_i) = \alpha -\log q$.  
Consider a particular block $i$, we measure how an adversary's queries affect the entropy of this block~(we can ignore the other blocks as they are independent).  
Let $q_w$ be a query asking if the stored value is $a_w$ and its corresponding response.  
Let $Q_{w_1},A_{w_1},..., Q_{w_q}, A_{w_q}$ be the random variables representing the queries and answers for an  adversary $\mathcal{A}$ making $q$ queries.  We assume a deterministic adversary (the adversary is unbounded and thus can compute the best possible queries).  The only dependence between $W_i$ and this view of the adversary is in $A_1,..., A_q$ so we can consider these binary responses.  Our goal is to count the total number of possible responses $A_{w_1},..., A_{w_q}$.  There are two basic cases for $A_{w_1},..., A_{w_q}$: the all zeros string and the case where some query returns $1$.  If some query $Q_{w*}$ returns $1$ then all other $Q_{w_i} = Q_{w*}$ will return $1$ but no other query returns $1$.  These responses can be removed as the response is deterministic.  Let $A'$ represent the sequence with all duplicate queries removed.  This sequence has at most a single $1$.  Thus, the total number of possible responses is $q+1$~(including the duplicates does not change the number of possible responses).  Thus, we have the following,
\begin{align*}
\Hav(W_i | View(S)) &= \Hav(W_i| Q_{w_1}, A_{w_1},..., Q_{w_q}, A_{w_q})\\
&=\Hav(W_i | A_{w_1},..., A_{w_q})\\
&=\Hav(W_i |A') \\
&=\Hoo(W_i) - \log |A'|\\
&=\alpha - \log |A'|\\
&=\alpha - \log (q+1)
\end{align*}
Where the fourth line follows from the third by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
This argument holds for all $i$.  This completes the proof.
\end{proof}
In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} consider block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  This is a subset of the distributions in \clref{cl:independent high ent}.

We now consider more complicated~(realistic) distributions where blocks are not independent.  We begin with distributions that are block unguessable.

Note the total entropy of a source in \clref{cl:each block from single seed} is $e$, so this is a family of distributions with total entropy $\omega(\log n)$ where \consref{cons:first construction} is secure.  This claims rests on there being no easy ``entry'' point to the distribution.  This is not always the case.  Indeed it is possible for some blocks to have very high entropy but lose all of it after equality queries.

\section{Discussion}
\label{sec:discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).

@@

\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.  The first is that Hamming distance is over an alphabet of exponential size, which precludes use in some applications.  The second is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.  Lastly, we obtain only a single bit from each block of $W_i$ which seems sub optimum.
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  
We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.  In \apref{sec:characterize} we provide discussion on the types of sources that satisfy \defref{def:block guessable}.
To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.  Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.  First note that $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$.  
Define the distribution $X$ as follows:
\[X_i = 
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}_X(\cdot, \cdot)}(C)$~(\defref{def:obf}).
\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ cannot distinguish between $C$ and $C'$.  That is, $S^{\mathcal{O}_X(\cdot, \cdot)}(C) \approx S^{\mathcal{O}_X(\cdot, \cdot)}(C')$.
This is done in \lemref{lem:sim cannot distinguish}.
% the following steps:
%\begin{itemize}
%%\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
%%\item Assume that the simulator has knowledge of $C_{\mathcal{I}^c}$.
%\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the simulator's view~(\lemref{lem:codewords in I close}).
%\item The two distributions $C$ and $C'$ are indistinguishable given the simulator's view~(\bnote{this needs to be written down.})
%\item The set of codewords $C| View(S) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(S)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
%\item Any adversary given $C$ or a fresh $C'$ cannot statistically distinguish.
%\end{itemize}
\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$~(\defref{def:obf}).
\end{itemize}

\noindent Together these arguments allow us to conclude:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.  Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

@@

\subsection{Discussion}
\label{sec:discussion}
Security of \consref{cons:first construction} relies on a large number of dimensions which are unpredictable.  Correction occurs for a small number of dimensions that are allowed to vary completely.  As described in \secref{sec:sec of construction}, \consref{cons:first construction} is not secure for an arbitrary min-entropy source, it must contain a significant number of dimensions that are hard to guess by equality queries~(meaning they have min-entropy).

@@

\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.   The first is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.  Second, we obtain only a single bit from each block of $W_i$ which seems sub optimum.  Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications. We begin to address this weakness in the next section.\bnote{come back to this linking language}

\section{Sample-then-Obfuscate}
\consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.  In this section, we present a generalization of where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.  This has two advantages, first it simplifies the type of sources we consider as we no longer need high entropy blocks.  Second, it allows us to decrease the size of each block from exponential to an arbitrary super polynomial.  Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.  In ordering for sampling to work properly, we need a source that is likely contribute some entropy from a randomly chosen block.

\begin{definition}
\label{def:unordered source}
A distribution $W = W_1,..., W_\gamma$ is called a $(\alpha, \beta)$-unordered block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
\[
\forall i\in \mathcal{I}, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}, W_{i+1}=w_{i+1},..., W_\gamma = w_\gamma) \geq \alpha.
\]
\end{definition}

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.  This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we will achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.  We will use an algorithm that draws random samples from block sources.  Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that outputs $\eta$ random and unique indices of $\{1,..., \gamma\}$ and let $r_{sam}$ the number of required coins for $\sample$.
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$ and $\gamma = Omega(n )$.  Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.   Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.  Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta$.  Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $c\leftarrow C$.
\item For $i=1,..., \ell$:
\begin{itemize}
\item Sample $\lambda_i\overset{\$}\leftarrow \zo^{r_{sam}}$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\eta,\gamma}( \lambda_i)$
\item If $c_i = 0$: 
\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\subitem Set $\rho_i = \mathcal{O}(I_{w_i})$.
\subitem Set $p_i = \rho_i, \lambda_i$.
\item If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
\subitem Let $p_i = \mathcal{O}(I_{r_i}) \lambda_i$.
\end{itemize}
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ 
\item For $i=1,..., \ell$:
\begin{itemize}
\item Parse $p_i$ as $\rho_i, \lambda_i$.
\item Set $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_{\gamma, \eta}(\lambda_i)$.
\item Set $v_i = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
\item If $\rho_i(w_i') = 1$ set $c_i' = 0$.
\item Else set $c_i' = 1$.
\end{itemize}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.37in}
\end{minipage} 
\end{tabular}
\end{center}
\end{construction}

The main change in \consref{cons:sampling} is that the obfuscated values are concatenated alphabet symbols of $W$.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.  There is a crucial difference, our use of a computationally-secure primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.  In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.  Our construction uses the na\"{i}ve sampler that takes truly random samples, the analysis is essentially the same for more sophisticated samplers that use fewer random bits.  Goldreich provides an accessible introduction to samplers~\cite{goldreich1997sample}.

As before we must show security and correctness of \consref{cons:sampling}.  For security, the main argument is that each of the $v_i$ has enough entropy to be unguessable.  For correctness we must show that the induced error rate in $v$ and $v'$ is a small constant so that $c'$ will be corrected to $c$ with overwhelming probability.

\subsection{Security of \consref{cons:sampling}}
Consider a source where most blocks have some entropy~(conditioned on the rest).
In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has super-logarithmic entropy on its own.  A sampler will select enough good blocks almost all the time, meaning if we take enough samples we obtain a super-logarithmic amount of entropy.  This means that  $V_1,..., V_\ell$ is a block-unguessable distribution~(by \clref{cl:all blocks entropy}) and security follows by \thref{thm:security of cons}.

\begin{lemma}
\label{lem:sampling works}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1)))$-unordered block source.  Let $\eta = \Omega(\log n)$. Consider some fixed $i$, the distribution $V_{i}, \Lambda_i$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{r_{sam}}$ where for all $u\in U_{r_{sam}}$ $V' | U_{r_{sam}}=u$, $\Hoo(V' | U_{r_{sam}}=u) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.
\end{lemma}
\begin{proof}
By~\cite[Lemma 9]{vadhan2003constructing}, noting that the truly random sampler is optimum in necessary samples and we take $\eta = \Omega(\log n)$ samples.  \bnote{need someone to check parameters, I am fairly sure of the quality of the statement}
\end{proof}

\begin{corollary}
\label{cor:samp sec}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.  Let $\eta = \Omega(\log n)$.  
The distribution $V, \Lambda$ is $\epsilon_{sam}(\ell (\ngl(n) +2^{-\Omega(n)})) = \ngl(n)$-close to a distribution $V', U_{\ell\times r_{sam}}$ where for $u\in U_{\ell\times r_{sam}}$ for all $i$, $\Hoo(V_i' | U_{\ell\times r_{sam}} =u)\geq \alpha'$.
\end{corollary}
\begin{proof}
Union bound over the statistical distance in \lemref{lem:sampling works}.
\end{proof}

\begin{corollary}
\label{cor:v are unguessable}
Let $q = \poly(n)$, there exists some $\alpha'' = \omega(\log n)$ such that distribution $V' , U_{\ell\times r_{sam}}$ is a $(q, \alpha'', 0)$-block unguessable distribution.
\end{corollary}
\begin{proof}
Result of \clref{cl:all blocks entropy}.
\end{proof}

\begin{corollary}
\label{cor:samp unguess}
Let $n, Z, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |Z|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha''-1)}) = \ngl(n)$.
\end{corollary}
\begin{proof}
Result of \corref{cor:v are unguessable} and \thref{thm:security of cons}.
\end{proof}

\subsection{Correctness of \consref{cons:sampling}}
The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.  Let $t'$ be the capacity of $C$.  To show correctness we must show that with overwhelming probability $\dis(v, v')\leq t'$.  Let $t$ be the number of supported errors between $w$ and $w'$.  Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
% In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.  Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.  Then 
\begin{align*}
\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c(\gamma-\eta)/\eta}{\gamma-i}\right)\\
&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\right) \\
&\geq \left(1-\frac{c}{\eta}\right)^{\eta} =\left( \left(1-\frac{c}{\eta}\right)^{\eta/c}\right)^c\geq \frac{1}{4}^c
\end{align*} 
Thus, by setting $c = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.

\begin{lemma}
Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.  Let $c = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq c(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.
\end{lemma}
\begin{proof}
With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^c = t'/(2\eta)$. By the Chernoff bound, we have
\begin{align*}
\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \ell}) 
\end{align*}
\end{proof}

\begin{corollary}
Let $\ell = \omega(\log n)$ and let $C\subset\zo^\ell$ and  be a code that corrects $t' = \Theta(\ell)$ $0\rightarrow 1$ bit errors.  Then when 
\[
\dis(w, w')\leq \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = O(\frac{\gamma-\eta}{\eta}) = O(\gamma/\eta)
\] 
and $(R, P)\leftarrow \gen(w)$, then 
\[
\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\ell}) = 1-\ngl(n).
\]
That is, \consref{cons:sampling} is correct with error at most $\ngl(n)$.

\end{corollary}
\subsection{Discussion of \consref{cons:sampling}}
We now show that \consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.  For security of an unordered block source we needed both $\alpha = \Theta(1)$ and $\beta\leq \gamma/2-\Omega(1)$.  This means that the overall required entropy of $\Hoo(W) = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors
This yields:
\begin{align*}
gap &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |Z|\\
&= \Theta(\gamma) - O(\gamma/\eta) \log |Z|\\
\end{align*}
That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for any fixed $Z$ we can set $\eta = \omega(\log n)$ and $\eta = o(\log |Z|)$).  If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $Z$.
\bibliographystyle{alpha}
\bibliography{crypto}
